### 2014-03-01 paper/real.tex
fix comparison w/ c in haskell subsection

\subsection{Haskell}
\label{sec:real:hs}
While the C embedding closely resembles the specification language of
Section~\ref{sec:retrofit}, in our Haskell IFC embedding we leverage
Haskell's strong data abstraction and static type system, monadic
approach to effects, and lightweight concurrency to implement the
embedding in a more efficient manner, as library.

>>>>

\subsection{Haskell}
\label{sec:real:hs}
While the C embedding relies on hardware protection mechanisms to
implement the embedding of Section~\ref{sec:retrofit}, in our Haskell
IFC embedding we leverage Haskell's strong data abstraction and static
type system, monadic approach to effects, and lightweight concurrency
to implement the embedding in a more efficient manner, as library.
